%
% File acl2012.tex
%
% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
%%
%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn


\documentclass[11pt]{article}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url} 


\usepackage{lingmacros}
\usepackage{tree-dvips}
\usepackage{graphicx}


\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Predicting Viewer Reactions of Debate Performances}

\author{Peter Enns \\
  Linguistics Department \\
  University of Maryland \\
  {\tt slunk@terpmail.umd.edu} \\\And
  Isaac Julien \\
  Computer Science Department \\
  University of Maryland \\
  {\tt ijulien6@gmail.com} \\ \\\And
  Alex Memory \\
  Computer Science Department \\
  University of Maryland \\
  {\tt memory@cs.umd.edu} \\
  }

\date{}

\begin{document}
\maketitle
\begin{abstract}
  We predict reactions of viewers to debate performances.  We did this and that.
\end{abstract}

\section{Introduction}
\input{introduction}

\section{Project Plan}
\input{project_plan}

\section{Data and Resources}
\input{data_and_resources}

\section{The Problem}
\input{problem}

\section{Models and Algorithms}
\input{models_and_algorithms}

\section{Evaluation}
\input{evaluation}

\section{Discussion}
\input{discussion}

\section{Challenges}
\input{challenges}

\section*{Acknowledgments}
The authors thank Phil Resnik for the debate corpus and data.

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

\end{document}
